Deep Reinforcement Learning for Conservation Decisions

### 2021-06-10 manuscript/manuscript.Rmd
Keeping up to date

Neural networks become useful in RL when the environment has a large observation-action space^[Conventionally, an observation-action space is considered to be large when it is non-tabular, i.e. cannot be represented in a computationally tractable table.], which happens frequently with realistic decision-making problems. 
Whenever there is a need for an agent to approximate some function, say a policy function, neural networks can be used in this capacity due to their property of being general function approximators [@universalapproximators].
Although there being other function approximators that can be used in RL, e.g. Gaussian processes [@grande14], neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@briefsurveydrl].
In this paper, we will focus on model-free RL approaches that employ neural networks.
We provide more conceptual and practical background on model-free deep RL in Appendix A and B respectively.

@@

## RL Formalism

@@

Although there are RL-based methods for infinite horizon problems, i.e. when $H=\infty$, we will only present episodic or finite horizon POMDPs in this study.

>>>>

Neural networks become useful in RL when the environment has a large observation-action space^[Conventionally, an observation-action space is considered to be large when it is non-tabular, i.e. cannot be represented in a computationally tractable table.], which happens frequently with realistic decision-making problems. 
Whenever there is a need for an agent to approximate some function, say a policy function, neural networks can be used in this capacity due to their property of being general function approximators [@universalapproximators].
Although there being other function approximators that can be used in RL, e.g. Gaussian processes [@grande14], neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@briefsurveydrl].
In this paper, we will focus on model-free RL approaches that employ neural networks. <!-- ML: put in sentence to introduce table here-->
We provide more conceptual and practical background on model-free deep RL in Appendix A and B respectively.

@@

## RL Objective

@@

Although there are RL-based methods for infinite horizon problems, i.e. when $H=\infty$, we will only present episodic or finite horizon POMDPs in this study.
<!-- Put in a sentence to point to the appendix -->
